InteroceptionStudy_GPValidation

### 2022-12-03 Figures.Rmd
test for Review
recover the power analyses files

  text=element_text(size = 14, family = "sans"),
  axis.text.x = element_text(size = 14*(sf+.5), family = "sans", colour = "black",),
  axis.text.y = element_text(size = 14*(sf+.5), family = "sans", colour = "black"),

@@

plots_paper$interaction_ar_vl <- plots_paper$interaction_ar_vl +
   theme_classic()+
   p$graphstyle_int
   # change leged title
   guides(linetype=guide_legend(title="New Legend Title"), fill = guide_legend(title="New Legend Title"))

plots_paper$interaction_ar_vl

@@

@@

db_full4new_stim_screen_pupil_nopract
plots_paper$pupil_correlation <- db_full4new_stim_screen_pupil_nopract %>%
  subset(!is.na(mediansplit_sample_valence2))%>%
   subset(Group == "NT")%>%
  # subset(pupil_outlier == FALSE)%>%
  # subset( arousal_outler == FALSE & !is.na(Alexithymia))%>%
  # subset(!is.na(Alexithymia))%>%
  # subset(ssid_num<500)%>%
    # group_by(ssid,Alexithymia, is_valence_high)%>%
   group_by(ssid, mediansplit_sample_valence2)%>%
    mutate(cortest = cor(arousal_c, pup_basCor, use = "complete"))%>%
    summarise_if(is.numeric, mean, na.rm = TRUE)%>%
        ggplot(aes(mediansplit_sample_valence2, cortest, fill = mediansplit_sample_valence2, 
                   color = mediansplit_sample_valence2))+
           geom_bar(aes(linetype = mediansplit_sample_valence2), 
                    stat="summary", fun.y = "mean", alpha = .3, width = .5, size = 2)+
    geom_jitter(width = .1, alpha = .1)+
        stat_summary( geom = 'pointrange', color = "black")+
          stat_summary(aes(group = ssid), geom = 'line', color = "black", alpha = .3)+
    ylab("R pupil vs self report arousal")+
  theme_classic()+
  geom_hline(yintercept = 0, linetype = 'dashed', alpha = .2)+
   # ggpubr::stat_compare_means(paired = TRUE)+
  ggpubr::stat_compare_means(method = 't.test',
                             symnum.args = symnum.args)+
   ylab(expression("Pupil vs subjective arousal ("*rho * ")"))+
   xlab("Subjective valence")

 plots_paper$pupil_correlation<- plots_paper$pupil_correlation+ p$graphstyle+
    scale_fill_brewer(palette = "Dark2")+
     scale_color_brewer(palette = "Dark2")

@@

# try with cluster]

@@

@@

@@

@@

plots_paper$interaction_SCR<- plots_paper$interaction_SCR +
# plots_paper$interaction_ar_vl +
  theme_classic()+
  p$graphstyle_int+
  xlab("Subjective arousal (z)")+
  ylab("Phasic SCR (log)")

@@

  plots_paper$interaction_SCR+

@@

```{r}
library(patchwork)

plot_patch1<- (plots_paper$interaction_ar_vl +
plots_paper$pupil_correlation +
plots_paper$pupil_course +
plots_timecourse$eff_size_pup_amp+
  plots_paper$interaction_SCR+
  plots_paper$bio_HR)+
  plot_layout(nrow = 3)+
  plot_annotation(tag_levels = "A")

@@

ggsave("patch_plot1.png", plot_patch1, device = "png", width = 15,height = 15, dpi = 800)
ggsave("patch_plot1.tiff", plot_patch1, device = "tiff", width = 15,height = 15, dpi = 800)
```

@@

scater_pupil_HR<- db_full6new_hr_fix_stim_nt1.1 %>%
  subset(!is.na(stimDescription))%>%
  subset(!is.na(mediansplit_ground_valence))%>%
  group_by(stimIAPS,mediansplit_ground_valence, stimDescription)%>%
  subset(Bio_Mean_HR_dif_outl!= "outlier")%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
  ggplot(aes(Bio_Mean_HR_dif, pup_basCor))+
  geom_point(aes(color = mediansplit_ground_valence), size = 2, alpha = .6)+
  geom_text(aes(label = stimDescription,olor = mediansplit_ground_valence), alpha = .3)+
  geom_smooth(method = 'lm', se = F)+
  ggpubr::stat_cor()+
  xlab(expression("Average "*Delta*" heart rate (bpm)"))+
  # xlab("Average heart rate difference")+
  ylab("Average pupil change (au)")+
  p$graphstyle

@@

fix_dur_byval<-
db_full4new_stim_screen_pupil_nopract %>%
  subset(pp_arousal_outler== FALSE)%>%
  subset(Group == "NT")%>%
  subset(pupil_outlier == FALSE)%>%
  subset(!is.na(Alexithymia))%>%
  # group_by(mediansplit_ground_valence)%>%
  # mutate(pup_basCor_mean = mean(pup_basCor, na.rm = TRUE), sd_pup = sd(pup_basCor, na.rm = TRUE), subj = n())%>%
  group_by(ssid, mediansplit_ground_valence)%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
  # group_by(mediansplit_ground_valence)%>%
  # mutate(pup_basCor_se = sd_pup/(sqrt(subj)))%>%
  ggplot(aes(mediansplit_ground_valence, mean_fix_dur))+
  # geom_bar(stat="summary", fun.y = "mean", alpha = .4, color = FALSE)+
      geom_jitter(width = .1, alpha=.2)+
  stat_summary(geom = 'pointrange',  size = 1, colour = "Black") +
  # geom_errorbar(aes(ymin = pup_basCor_mean-pup_basCor_se, ymax = pup_basCor_mean+pup_basCor_se ))+
  geom_line(aes(group = ssid), alpha = .1)+
  p$graphstyle+
  theme(axis.text.x = element_text(size = 14, angle = 45), axis.title.x = element_blank())+
  xlab("Valence")+
  ylab("Average fixation duration (ms)")+
  # ylab("Baseline corrected pupil")+

@@

? ggpubr::stat_compare_means
fix_dur_byval

>>>>

  text=element_text(size = 14),
  axis.text.x = element_text(size = 14*(sf+.5), colour = "black",),
  axis.text.y = element_text(size = 14*(sf+.5), colour = "black"),

@@

plots_paper$interaction_ar_vl <- plots_paper$interaction_ar_vl +
   theme_classic()+
   p$graphstyle_int
   # change leged title
   # guides(linetype=guide_legend(title="New Legend Title"), fill = guide_legend(title="New Legend Title"))

plots_paper$interaction_ar_vl <- plots_paper$interaction_ar_vl +
 guides(title="valence",
        fill = guide_legend(title="valence"),
        color = guide_legend(title="valence"),
        linetype = guide_legend(title="valence"))

@@

plots_paper$interaction_ar_vl
```

@@

db_full4new_stim_screen_pupil_nopract
plots_paper$pupil_correlation <- db_full4new_stim_screen_pupil_nopract %>%
  subset(!is.na(mediansplit_sample_valence2))%>%
   subset(Group == "NT")%>%
  # subset(pupil_outlier == FALSE)%>%
  # subset( arousal_outler == FALSE & !is.na(Alexithymia))%>%
  # subset(!is.na(Alexithymia))%>%
  # subset(ssid_num<500)%>%
    # group_by(ssid,Alexithymia, is_valence_high)%>%
   group_by(ssid, mediansplit_sample_valence2)%>%
    mutate(cortest = cor(arousal_c, pup_basCor, use = "complete"))%>%
    summarise_if(is.numeric, mean, na.rm = TRUE)%>%
        ggplot(aes(mediansplit_sample_valence2, cortest, fill = mediansplit_sample_valence2, 
                   color = mediansplit_sample_valence2))+
           geom_bar(aes(linetype = mediansplit_sample_valence2), 
                    stat="summary", fun.y = "mean", alpha = .3, width = .5, size = 2)+
    geom_jitter(width = .1, alpha = .1)+
        stat_summary( geom = 'pointrange', color = "black")+
          stat_summary(aes(group = ssid), geom = 'line', color = "black", alpha = .3)+
    ylab("R pupil vs self report arousal")+
  theme_classic()+
  geom_hline(yintercept = 0, linetype = 'dashed', alpha = .2)+
   # ggpubr::stat_compare_means(paired = TRUE)+
  ggpubr::stat_compare_means(method = 't.test',
                             symnum.args = symnum.args)+
   ylab(paste0("Pupil vs subjective \n arousal (cor)"))+
   xlab("Subjective valence")
   0
 plots_paper$pupil_correlation<- plots_paper$pupil_correlation+ p$graphstyle+
    scale_fill_brewer(palette = "Dark2")+
     scale_color_brewer(palette = "Dark2")

@@

```
# try with cluster]

@@

plots_paper$interaction_ar_vl<

@@

timecourse_60bin_result_df

@@

plots_timecourse$eff_size_pup_amp+ p$graphstyle

@@

plots_paper$interaction_SCR<- plots_paper$interaction_SCR +
# plots_paper$interaction_ar_vl +
  theme_classic()+
  p$graphstyle_int+
  xlab("Subjective arousal (z)")+
  ylab("Phasic SCR (log)")+
  guides(title="valence",
        fill = guide_legend(title="valence"),
        color = guide_legend(title="valence"),
        linetype = guide_legend(title="valence"))

@@

@@

```{r}
library(tidyverse)

p$graphstyle <-  theme(#base plot theme

  # axis lines
  axis.line.y = element_line(color="black"),
  axis.line.x = element_line(color="black"),

  text=element_text(size = 14),
  axis.text.x = element_text(size = 14*(sf+.5), colour = "black",),
  axis.text.y = element_text(size = 14*(sf+.5), colour = "black"),

  # panel
  panel.grid.major = element_blank(),
  panel.background = element_blank(),
  # panel.background = element_rect(fill="transparent"),
  # panel.border = element_rect(fill="transparent"),
  # strip shades (reco rectagles)
   strip.background = element_blank(),

  #legend.text = element_text(size = 10*sf),
  legend.title=element_blank(),
  #legend.text = element_blank(),
  #axis.ticks = element_blank(),
)
library(patchwork)

@@

plots_paper$pupil_correlation <-plots_paper$pupil_correlation +
  theme(legend.position = "none")
fix_dur_byval<-
fix_dur_byval+theme(legend.position = "none")
part1<- (plots_paper$interaction_ar_vl |plots_paper$pupil_correlation |plots_timecourse$eff_size_pup_amp)/
  (plots_paper$interaction_SCR| plots_paper$bio_HR |scater_pupil_HR)

part2<-    (correlation_plot+fix_dur_byval)+plot_layout(ncol = 2, widths = c(3,1))

part3<- (part1/
part2)
  # plot_layout(nrow = 3)+
  plot_annotation(tag_levels = "A", widths = c(2,1,1), heigths = c(1,1,2))

ggsave("patch_plot1.png", plot_patch1, device = "png", width = 15,height = 15, dpi = 800)
ggsave("patch_plot1.tiff", plot_patch1, device = "tiff", width = 15,height = 15, dpi = 800)

ggsave("part3.tiff", part3, device = "tiff", width = 15,height = 12, dpi = 800)
```

@@

scater_pupil_HR<- db_full6new_hr_fix_stim_nt1.1 %>%
  subset(!is.na(stimDescription))%>%
  subset(!is.na(mediansplit_ground_valence))%>%
  group_by(stimIAPS,mediansplit_ground_valence, stimDescription)%>%
  subset(Bio_Mean_HR_dif_outl!= "outlier")%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
  ggplot(aes(Bio_Mean_HR_dif, pup_basCor))+
  geom_point(aes(color = mediansplit_ground_valence), size = 2, alpha = .6)+
  geom_text(aes(label = stimDescription,olor = mediansplit_ground_valence), alpha = .3)+
  geom_smooth(method = 'lm', se = F)+
  ggpubr::stat_cor()+
  xlab(expression("Mean "*Delta*" heart rate (bpm)"))+
  # xlab("Average heart rate difference")+
  ylab("Mean pupil \n change (au)")+
  p$graphstyle

@@

fix_dur_byval<-
db_full4new_stim_screen_pupil_nopract %>%
  subset(pp_arousal_outler== FALSE)%>%
  subset(Group == "NT")%>%
  subset(pupil_outlier == FALSE)%>%
  subset(!is.na(Alexithymia))%>%
  # group_by(mediansplit_ground_valence)%>%
  # mutate(pup_basCor_mean = mean(pup_basCor, na.rm = TRUE), sd_pup = sd(pup_basCor, na.rm = TRUE), subj = n())%>%
  group_by(ssid, mediansplit_ground_valence)%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)%>%
  # group_by(mediansplit_ground_valence)%>%
  # mutate(pup_basCor_se = sd_pup/(sqrt(subj)))%>%
  ggplot(aes(mediansplit_ground_valence, mean_fix_dur, color = mediansplit_ground_valence, fill = mediansplit_ground_valence))+
  # geom_bar(stat="summary", fun.y = "mean", alpha = .4, color = FALSE)+
      geom_jitter(width = .1, alpha=.2)+
  stat_summary(geom = 'pointrange',  size = 1, colour = "Black") +
  # geom_errorbar(aes(ymin = pup_basCor_mean-pup_basCor_se, ymax = pup_basCor_mean+pup_basCor_se ))+
  geom_line(aes(group = ssid), alpha = .1)+
  p$graphstyle+
  theme(axis.text.x = element_text(size = 14, angle = 45), axis.title.x = element_blank())+
  xlab("Valence")+
  ylab(paste0("Mean fixation \n duration (ms)"))+
  # ylab("Baseline corrected pupil")+

@@

# ? ggpubr::stat_compare_means
fix_dur_byval

### 2022-12-03 IAPS_PREPROCESSING_2021_1_56_357_611_616.Rmd
test for Review
recover the power analyses files

write_csv(tmp.df4_sum_full_bio_hr_self_parsed, 'tmp.df4_sum_full_bio_hr_self_parsed_356_357_611_616.csv')
write_csv(tmp.df4, 'tmp.df4_timeseries_356_357_611_616.csv')
```

>>>>

write_csv(tmp.df4_sum_full_bio_hr_self_parsed, 'tmp.df4_sum_full_bio_hr_self_parsed_356_357_611_616.csv')
write_csv(tmp.df4, 'tmp.df4_timeseries_356_357_611_616.csv')

save.image("~/OneDrive - Nexus365/InteroStudy2020/analysis/DataAnalysisJanuary2020/DataAnalysisJan2020/356_357_611_616_preprocessing.RData")
```
